% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
A search for Supersymmetry in the jets and missing energy final state is
described using the CMS detector at the LHC, and the full 18.5~\fb 
`Parked' dataset
of $\sqrt{s} = 8$~\tev proton-proton collisions. This dataset was collected
using experimental, low-threshold triggers to increase sensitivity to softly
decaying new physics signatures. The search makes use of the
kinematic variable, \alphat, to reduce contributions from QCD multijet
processes by many orders of magnitude, to a level considered negligible.
Remaining background sources originate from electroweak decays of heavy bosons
and top quarks, and are
estimated using a data-driven technique employing dedicated control regions. To
maintain sensitivity to a broad range of potential
manifestations
of Supersymmetry, the analysis categorises events in dimensions of the scalar
sum of hadronic energy, the number of jets and the number of jets originating
from b quarks.
While this analysis aims to remain inclusive to many hadronically decaying SUSY
signatures, the work in this thesis exploits the low energy thresholds of the
`Parked' triggers and therefore considers models with compressed mass spectra.
As no statistically significant excess is observed, results are
interpreted within the context of decays of stop
particles relevant in the compressed spectra region. Stop decays to charm
quarks and via four-body decays to fermions are considered, both with the weakly
interacting Lightest SUSY Particle in the final state.
Limits are placed on the mass of the stop of up to 275 GeV for the charm decay
and up to 250 GeV for the four-body decay. Natural units ($\hbar = c = 1$) are
used throughout this work.
\end{abstract}

