\chapter{Interpretation}

% **************************** Define Graphics Path **************************
\ifpdf
    \graphicspath{{Chapter9/Figs/Raster/}{Chapter9/Figs/PDF/}{Chapter9/Figs/}}
\else
    \graphicspath{{Chapter9/Figs/Vector/}{Chapter9/Figs/}}
\fi

%********************************** % First Section  *************************************
\section{Signal Acceptance}  %Section - 1.1 
\label{sec:interpretation_acceptance}
Show acceptance for each model
Briefly explain any features in each, particularly for mass-degenerate models

%********************************** % Second Section  *************************************
\section{Systematic Uncertainties on Signal Acceptance }  %Section - 1.2
\label{sec:interpretation_uncertainties}

Fully reliant on MC for signal interpretations.
A number of different considerations

\subsection{Jet energy scale}
\subsection{Initial State Radiation}
\subsection{Btag scale factors}
\subsection{PDF}
\subsection{MHT/MET cleaning cut}
\subsection{Dead ECAL Filter}
\subsection{Shape systematics}
\subsection{Integrated Luminosity}
\subsection{Number of MC Partons}
\subsection{Any others?}
\subsection{Summary}

%********************************** % Third Section  *************************************
\section{Limits on models of Supersymmetry}  %Section - 1.3
\label{sec:interpretation_limits}

\subsection{Overview of limit setting procedure}
Using green and blue band fits for expected and observed
considering MC stats of signal MC samples
point-by-point systematics

discussion of CLs method. Look up `CLs 4 LHC'

\subsection{Limits}
different limits for the various models


%********************************** % Fourth Section  *************************************
\section{Interpretation of excesses}
\label{sec:interpretation_excess}
best fit points in T2cc
global context?
p-values with SUSY assumption? is that even a thing? who knows? who cares.