\chapter{Object Definitions}

% **************************** Define Graphics Path **************************
\ifpdf
    \graphicspath{{Chapter4/Figs/Raster/}{Chapter4/Figs/PDF/}{Chapter4/Figs/}}
\else
    \graphicspath{{Chapter4/Figs/Vector/}{Chapter4/Figs/}}
\fi


%********************************** % First Section  *************************************
\section{Introduction}  %Section - 1.1 
\label{sec:objects_introduction}

Physics objects are observed as energy deposits in the various detector 
subsystems throughout the CMS detector. Specific definitions for the different 
objects are provided by the Physics Object Groups (POGs) and are used in this 
analysis. The following sections describe the objects used.


%********************************** % Second Section  *************************************
\section{Jets}  %Section - 1.2
\label{sec:objects_jets}

Jets are produced when a single quark or gluon is produced, subsequently 
hadronizing and showering throughout the calorimeter systems. Energy deposits in
the hadronic calorimeter are clustered using the anti$-k_T$ algorithm [ref] with
a 0.5 cone size parameter. The raw energy measurements can be affected by 
effects from overlapping pp collisions, known as pileup (PU) [first place 
mentioned?], therefore corrections are made to account for this. Clustered jets 
are also corrected to establish a uniform response in $\eta$ and \Pt.
Table~\ref{tab:jet_id_loose} summarises the ID requirements used in this 
analysis, which correspond to the ``Loose'' working point [ref]. Jets are also 
corrected according to the L1FastJet, L2, L3, and L2L3Residual corrections [ref].

\begin{table}[!ht]
  \caption{Criteria for the ``loose'' jet ID working point.\label{tab:jet_id_loose}REWORD}
  \footnotesize
  \begin{center}
    \begin{tabular}{ll}
      \hline
      \hline
      Requirement                & Definition                                                       \\
      \hline
      f$_{HPD} < 0.98$           & Fractional contribution from the ``hottest'' Hybrid Photo Diode. \\
      f$_{EM} > 0.01$            & Minimum electromagnetic fractional component.                    \\
      N$^{90}_{\rm hits} \geq$ 2 & Number of channels containing at least 90\% of total energy      \\
      \hline
      \hline
    \end{tabular}
  \end{center}
\end{table}


\subsection{Tagging jets from b-quarks}

Jets originating from b-quarks can be identified using information from the 
vertex detector due to their increased lifetime with respect to light-quarks (u,
d, s, c). 
B-tagging algorithms are designed to determine the probability that a jet 
originates from a b-quark, given, amongst other properties, the jet's tracks
displacement from the primary 
vertex (PV). Each algorithm
calculates a value used to discriminate between a jet from a b-quark and a
light-quark.

The Combined Secondary Vertex (CSV) algorithm is used in this analysis,
using the ``Medium'' working point, or a discriminate threshold of $>0.679$. This 
working point corresponds to a mistag rate for gluons/light-quarks of 1\%, and a
pT dependent efficiency in the range of 60-70\% (plot?) [refs].

%********************************** % Third Section  *************************************
\section{Electrons}  %Section - 1.3
\label{sec:objects_electrons}



%********************************** % Fourth Section  *************************************
\section{Muons}  %Section - 1.4
\label{sec:objects_muons}
Muons are identified using the muon POGs Tight working point definition, as 
summarised in table~\ref{tab:muon-id}. This definition is used for both muon 
selection in the \mj and \mmj control regions, and the muon veto in the hadronic
signal region.

\begin{table}[ht!]
  \caption{Muon identification (Tight working point).\label{tab:muon-id}}
  \centering
  \footnotesize
  \begin{tabular}{ lcp{8cm} }
    \hline
    \hline
    Global Muon                            & True      & Muon object 
    is reconstructed from both hits in the muon systems and matched hits in the 
    silicon tracker \\
    PFMuon                                 & True      & FIXME \\
    $\chi^{2} /ndof$ of fit                & $<10$     & Goodness of fit 
    of the global muon track fit. Suppresses hadronic punch-through and muons 
    decaying in flight.\\
    Muon chamber hits                      & $>0$      & At least 1 hit in a 
    muon chamber. Suppresses hadronic punch-through and muons 
    decaying in flight.\\
    Muon station hits                      & $>1$      & Muon hits in at least 2
    muon stations. Suppresses punch-through and accidental track-to-segment matches.
    (Also makes consistent with trigger muon requirements.) \\
    Transverse impact $d_{xy}$             & $<0.2mm$ & Tracker track is close 
    to PV (define?) in the x-y plane. Helps suppress cosmic ray muons and muons 
    from decays in flight. \\
    Longitudinal dist $d_{z}$              & $<0.5mm$ & Tracker track is close 
    to PV in z-direction. Suppresses muons from cosmic rays, decays in flight 
    and PU. \\
    Pixel hits                             & $>0$      & At least 1 pixel hit. 
    Suppresses muons from decays in flight. \\
    Track layer hits                       & $>5$      & Guarantees good \Pt 
    measurement. \\
    PF Isolation ($\Delta\beta$ corrected) & $<0.12$   & Particle Flow based 
    isolation, based on a cone size of $\Delta R < 0.4$, with ``$\Delta \beta$'' 
    PU corrections applied. \\
    \hline
    \hline
  \end{tabular}
\end{table}

LOOKUP: ``muons from decays in flight''

%********************************** % Fifth Section  *************************************
\section{Photons}  %Section - 1.5
\label{sec:objects_photons}


%********************************** % Sixth Section  *************************************
\section{Energy Sums}  %Section - 1.6
\label{sec:objects_energy_sums}

\subsection{ET}
\subsection{HT}
\subsection{MET}
\subsection{MHT}

%********************************** % Seventh Section  *************************************
\section{Single Isolated Tracks}  %Section - 1.7
\label{sec:objects_sit}
Selection criteria for a single isolated track - used later in the analysis for soft-lepton/
had tau rejection