% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

% Henning 
% Zhaoxia - constant help at start
% Same with Bryn, Darren, Ted, Yossof etc.

% Thanks to Allan and Donal for being great housemates during out time at CERN.

% To all my friends that have helped me through not only my PhD, but every step of
% the way that got me here.

% Bristol students, particularly Jeson, Sam, Dan and Emyr.

% Mum and Dad and Jon - immediate family, and the rest.

\begin{spacing}{1}
As I sit here in my kitchen, after having read my thesis for what feels like
the
thousandth time, I'm left with the intimidating task of writing these final
words - intimidating because there is no possible way I can portray enough my
incredible grattitude to the countless number of people that have helped me
get to the point I find myself in today.

I would like to thank the many people I have had the pleasure of working with
over the last three and half years. In particular those in
the RA1 team, notably Darren Burton, Bryn Mathias, Yossof Eshaq, Edward
Laird and Zhaoxia Meng, each for the seemingly unending patience and help
they've shown me throughout my work. Of course, it is to Rob Bainbridge that I
owe an incredible deal - not only for his constant guidance and supervision
throughout our work together, but also for what is quite possibly the longest
skype conversation history since the dawn of the internet.
I also owe a great deal of thanks to my supervisor Henning Flaecher for helping
me throughout my PhD with continual support and challenging discussions. If I've
read this thesis a thousand times, Henning may be nearing two thousand, and for
that I extend great thanks.

My fellow PhD students with whom I've experienced both the highs and lows of
the PhD experience, have always been there to bring me back around with a laugh
and a beer. Especially Emyr Clement, Jeson Jacob, Sam Harnew, Daniel Souza and
Donal Hill - I thank you.

Also I am incredibly grateful to the many friends and housemates that have helped me, likely without
even realising the importance of their actions, by
providing such a welcome and great relief from the research world. There are
far too many of you to name, but I'm sure you know who you are.

Of course, I couldn't go a whole round of thanks without mentioning the big man
himself, Allan `Ken' Lehan. For the far too many evenings spent
drinking far too many whiskies and chain-watching far too many episodes of The
Wire, I am hugely grateful (despite most of Season 3 still being a hazey
memory). I take back everything I've ever said - you're alright.

Finally, I would like to extend the greatest of thanks to my family, without whom
I simply wouldn't be in the position I am, or the person I've become today.
There's not a day goes by that I'm not thankful to have such incredible parents
who have encouraged and believed in me always, without fail.
For your incredible never-ending love and support I will perpetually be in debt
to you.
\end{spacing}

\end{acknowledgements}

