%*******************************************************************************
%*********************************** First Chapter *****************************
%*******************************************************************************

\chapter{Introduction}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
\else
    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
\fi


%********************************** % First Section  *************************************
%Section - 1.1 
\label{sec:introduction_intro}

Our instinctive method of understanding is reductive - the idea of an
inventor attempting to make sense of the things around them is
that of toasters, clock radios, or even gearboxes broken down into
their smallest constituent parts to better understand what they're made of and,
ultimately, what's happening inside of them. This simple idea translates
perfectly to explain the work Particle Physicists undertake with
not simple everyday objects, but the Universe.

Since the fields inception, physicists have questioned the Universe
around us, and what it's made of. From the early research of scientists such as
Ernest Rutherford and Niels Bohr, the basic building
blocks of the universe have been searched for. For Particle Physicists, this is
the ultimate goal - a complete understanding of the nature of the Universe
at its most
fundamental level. If a description can be written of these fundamental
building blocks of
nature and how they interact, then ultimately we can understand
the Universe from the bottom up.

Currently, our best attempt of such a description comes from the intersection of
two
fields: Quantum Mechanics, the study of microscopic objects, and Relativity, the
study of very fast objects. The combination of these
two very different worlds gave birth to the field of Relativistic
Quantum Mechanics, and ultimately, the Standard Model (SM).

First proposed in the 1960's, the Standard Model attempts to describe the
properties of the fundamental constituents of matter, and outline their
interactions through three of the four fundamental forces of nature, as
described in chapter~\ref{ch:theory}.
By withstanding substantial scrutiny from countless experiments since its
inception, the Standard Model has proven itself to be an exceptional
triumph of modern physics.

Despite its continued accuracy, however,
the Standard Model fails to account for significant observations, for example
the absent description of gravity and the `other' 96\% of the
Universe - the so-called `Dark Sector'. In addition the Standard Model fails to
unify the fundamental forces at some higher mass scale, or predict the masses of
particles, such as
the newly discovered Higgs boson. Given how successfully it describes
what it can, the SM is widely considered as a smaller component of some greater,
all-encompassing theory. This belief has led many to use this distinct theory as
a building block on which extensions can be introduced to create Beyond the
Standard Model (BSM) theories - the goal being to fill the gaps in knowledge
left by the SM.

Of the plethora of BSM theories, one particularly well motivated extension is
Supersymmetry (SUSY). The supersymmetric extension to the Standard
Model introduces supersymmetryic particles (or `sparticles') differing from
their SM partners by half a unit of spin - described in greater detail in
chapter~\ref{ch:theory}. The addition of sparticles fixes
many of the Standard Model's problems, most notably that of the
divergent Higgs Mass, the Unification of the fundamental gauge couplings and,
crucially, provides a feasible candidate particle for the elusive Dark Matter
observed in abundance in the Universe.

Particle physics as a field has developed largely via a cat and mouse game,
played out between theorists and experimentalists. While theoretical physicists
have developed new theories and proposed new particles, experimentalists have
raced to build greater and more advanced experiments with which to discover
them.
Today, thanks to the incredible work of thousands of physicists and
engineers, we are able to test such BSM theories with the Large
Hadron Collider (LHC) in Geneva, Switzerland.

The LHC, described in chapter~\ref{ch:detector}, is a 27~km
circumference proton synchrotron, capable of colliding protons
at centre-of-mass energies far exceeding any previous experiment.
Using the LHC, it is possible to reproduce the conditions observed a short time
after the Big Bang, where the incredibly high energies present were able to
produce countless particles that wouldn't be visible in today's universe. If
such exotic particles are created in the proton-proton collisions performed at
the LHC, it is the goal of detector experiments such as the Compact Muon
Solenoid (CMS) to find them.

The CMS detector, also described in chapter~\ref{ch:detector}, is comprised of
multiple sub-detector systems, each designed
specifically to make precise measurements of the characteristics of the
different particles created in the fierce collisions. The detector is built such
that it provides almost
complete hermetic coverage to detect particles travelling in all directions
from the point of interaction. Energy deposits throughout the detector
subsystems are used to form physics objects, as summarised in
chapter~\ref{ch:objects}, themselves allowing the events to be categorised by
the physics processes present.

A key technique
for searches for SUSY is the study of global momentum imbalances,
which allows for the presence of weakly interacting particles to be inferred.
If sparticles were to be produced at the LHC they would likely decay immediately
to many well-understood SM particles, and finally the weakly interacting
`Lightest Supersymmetric Particle' (LSP) - the theory's Dark Matter candidate.
Of the many different possible supersymmetric decays, hadronic channels offer
the largest branching fractions, although can present some of the most
difficult experimental challenges. Hadronic searches are of interest given their
relatively simple and quick ability to provide sensitivity to early discovery at
hadronic colliders such as the LHC.

The work described in this thesis consists of such a search for SUSY particles
decaying to quarks and missing-energy. The analysis makes use of the full
`Parked' data sample collected throughout 2012, where experimental
triggers collected events with lower energy thresholds than the standard data
stream.
These lowered thresholds greatly improve analysis sensitivity to soft
physics
processes, such as those expected from SUSY scenarios with nearly degenerate
mass hierarchies. The data samples and corresponding MonteCarlo simulated
samples used in this analysis are detailed in chapter~\ref{ch:samples}.

The biggest obstacle to
searching for hadronic signatures of new physics, is dealing with the
overwhelming hadronic backgrounds from Quantum Chromodynamics (QCD). In this
analysis a powerful kinematic variable, \alphat, is used to differentiate
between such QCD and potential signal events. The analysis backgrounds,
selection and
the \alphat variable are described in detail in chapter~\ref{ch:analysis}. The
remaining SM sources of background are estimated using a data-driven transfer
technique from dedicated control regions, orthogonal to the search region, as
outlined in chapter~\ref{ch:background}. The results of the transfer technique
are included as part of a simultaneous likelihood model fit to the signal and
all control regions to determine final background counts as described in
chapter~\ref{ch:results}.

Given the vast number of potential manifestations of SUSY, sparticles may
decay in many different ways if produced. Accordingly, chapter~\ref{ch:results}
also gives the results of this analysis, categorising events in dimensions
of three different event-level variables: the total sum of visible transverse
hadronic energy, the number of jets and the number of b-tagged jets.
Specific analysis categories are used to produce targeted
interpretations of different potential final states, thereby maintaining a broad
sensitivity to SUSY production, however it may present itself in nature. As
motivated by Dark Matter observations, the interpretations presented in this
thesis represent two different decay channels of the produced \sTop
sparticle in the so-called `compressed' region, where the mass of the \sTop is
near-degenerate with that of the LSP. Accordingly, limits on the mass of
the \sTop and the LSP are produced. These interpretations
and discussions of the related efficiencies and systematics are presented in
chapter~\ref{ch:interpretation}, before final conclusions are made in
chapter~\ref{ch:conclusion}.

Natural units ($\hbar = c = 1$) are used throughout this work.

% The analysis presented in this thesis is one of many such searches for
% Supersymmetry performed at the LHC, each with the goal of understanding better
% the nature of the largest scale objects of the Universe, by studying its
% smallest.
